Road User video evidence of road traffic offences: Preliminary analysis of Operation Snap data and suggestions for a research agenda

### 2024-09-16 paper.qmd
Tests

---
title: "Road User video evidence of road traffic offences: Preliminary analysis of Operation Snap data and suggestions for a research agenda"
bibliography: [references.bib, opsnap.bib]
editor:
  markdown: 
    wrap: sentence
keywords: 
  - Road safety
  - Video evidence
  - Near misses
  - Operation Snap
  - Dangerous driving
  - Antisocial driving
date: last-modified
format:
  # html: default
  # docx: default
  # pdf: default
  arxiv-pdf:
    keep-tex: true
linenumbers: true # Add (continuous) line numbers?
doublespacing: false # Double space the PDF output?
runninghead: "Preprint" # The text on the top of each page of the output
authorcols: true # Should authors be listed in a single column (default) or in multiple columns (`authorcols: true`)
editor_options: 
  markdown: 
    wrap: sentence
execute: 
  echo: false
  warning: false
  cache: false
---

@@

```{r}
#| eval: false
#| echo: false
# quarto::quarto_render("paper.qmd", output_format = "pdf")
# file.copy("paper.pdf", "~/OneDrive/opsnap_leeds/paper-no-line-numbers-v11.pdf")
# quarto::quarto_render("paper.qmd", output_format = "arxiv-pdf")
# file.copy("paper.pdf", "paper-v11.pdf")
# file.copy("paper.pdf", "~/OneDrive/opsnap_leeds/paper-v11.pdf")
# quarto::quarto_render("paper.qmd", output_format = "docx")
# # file.copy("paper.docx", "~/OneDrive/opsnap_leeds/paper-v11.docx")
# file.copy("paper.docx", "paper-v11.docx")
# quarto::quarto_render("title.qmd", output_format = "arxiv-pdf")
# browseURL("title.pdf")
# system("gh release upload v1 --clobber paper-v11.pdf title.pdf")
# browseURL("paper.docx")
# # Install extension:
# system("quarto install extension mikemahoney218/quarto-arxiv")
# system("sudo apt install lmodern")
```

@@

```{r}
#| echo: false
#| include: false
library(rvest)
query = ".file-link a"
url = "https://www.westyorkshire.police.uk/SaferRoadsSubmissions"
files_available = read_html(url) |>
  html_nodes(query) |>
  html_text()
links_available = read_html(url) |>
  html_nodes(query) |>
  html_attr("href")
urls = paste0("https://www.westyorkshire.police.uk", links_available)
file_names = basename(links_available)
tibble::tibble(file_names) |>
  knitr::kable()

# In preparation for reading-in all data:
# date_str = format(Sys.Date(), "%Y-%m")
date_str = format(as.Date("2024-04-01"), "%Y-%m")
file_name = paste0("data/west-yorkshire/operation_snap_", date_str, ".csv")
```

@@

```{r}
#| label: tbl-raw
#| tbl-cap: "Random sample of 5 records from the raw data."
set.seed(24)
d_all |>
  sample_n(5) |>
  select(-district, -`offence_code`) |>
  mutate(date = as.Date(date)) |>
  arrange(date) |>
  rename_all(snakecase::to_title_case) |>
  knitr::kable() |>
  # Striped styling and tiny text to fit:
  kableExtra::kable_styling(latex_options = "striped") |>
  # Set column widths:
  kableExtra::column_spec(1, width = "3em") |>
  kableExtra::column_spec(2, width = "3em") |>
  kableExtra::column_spec(3, width = "3em") |>
  kableExtra::column_spec(4, width = "3em") |>
  kableExtra::column_spec(5, width = "9em") |>
  kableExtra::column_spec(6, width = "4em") |>
  kableExtra::column_spec(8, width = "8em")
```

>>>>

---
title: "Road User video evidence of road traffic offences: Preliminary analysis of Operation Snap data and suggestions for a research agenda"
bibliography: [references.bib, opsnap.bib]
editor:
  markdown: 
    wrap: sentence
# keywords: 
#   - Road safety
#   - Video evidence
#   - Near misses
#   - Operation Snap
#   - Dangerous driving
#   - Antisocial driving
date: last-modified
format:
  # html: default
  # docx: default
  # pdf: default
  arxiv-pdf:
    keep-tex: true
# linenumbers: true # Add (continuous) line numbers?
# doublespacing: false # Double space the PDF output?
# runninghead: "Preprint" # The text on the top of each page of the output
# authorcols: true # Should authors be listed in a single column (default) or in multiple columns (`authorcols: true`)
execute: 
  echo: false
  warning: false
  cache: false
---

@@

```{r}
#| eval: false
#| echo: false
# quarto::quarto_render("paper.qmd", output_format = "pdf")
# file.copy("paper.pdf", "~/OneDrive/opsnap_leeds/paper-no-line-numbers-v12.pdf")
# quarto::quarto_render("paper.qmd", output_format = "arxiv-pdf")
# file.copy("paper.pdf", "paper-v12.pdf")
# file.copy("paper.pdf", "~/OneDrive/opsnap_leeds/paper-v12.pdf")
# quarto::quarto_render("paper.qmd", output_format = "docx")
# # file.copy("paper.docx", "~/OneDrive/opsnap_leeds/paper-v12.docx")
# file.copy("paper.docx", "paper-v12.docx")
# quarto::quarto_render("title.qmd", output_format = "arxiv-pdf")
# browseURL("title.pdf")
# system("gh release upload v1 --clobber paper-v12.docx")
# browseURL("paper.docx")
# # Install extension:
# system("quarto install extension mikemahoney218/quarto-arxiv")
# system("sudo apt install lmodern")
```

@@

```{r}
#| echo: false
#| eval: false
library(rvest)
query = ".file-link a"
url = "https://www.westyorkshire.police.uk/SaferRoadsSubmissions"
files_available = read_html(url) |>
  html_nodes(query) |>
  html_text()
links_available = read_html(url) |>
  html_nodes(query) |>
  html_attr("href")
urls = paste0("https://www.westyorkshire.police.uk", links_available)
file_names = basename(links_available)
tibble::tibble(file_names) |>
  knitr::kable()
```

```{r}
#| include: false
# In preparation for reading-in all data:
# date_str = format(Sys.Date(), "%Y-%m")
date_str = format(as.Date("2024-04-01"), "%Y-%m")
file_name = paste0("data/west-yorkshire/operation_snap_", date_str, ".csv")
```

@@

```{r}
#| label: tbl-raw
#| tbl-cap: "Random sample of 5 records from the raw data."
set.seed(24)
d_all |>
  sample_n(5) |>
  select(-district, -`offence_code`) |>
  mutate(date = as.Date(date)) |>
  arrange(date) |>
  rename_all(snakecase::to_title_case) |>
  knitr::kable()

  # # For PDF:
  # #  |>
  # # Striped styling and tiny text to fit:
  # kableExtra::kable_styling(latex_options = "striped") |>
  # # Set column widths:
  # kableExtra::column_spec(1, width = "3em") |>
  # kableExtra::column_spec(2, width = "3em") |>
  # kableExtra::column_spec(3, width = "3em") |>
  # kableExtra::column_spec(4, width = "3em") |>
  # kableExtra::column_spec(5, width = "9em") |>
  # kableExtra::column_spec(6, width = "4em") |>
  # kableExtra::column_spec(8, width = "8em")
```
